---
title: "GIS test"
output: html_notebook
---

```{r}
library(sf)
dir_data <- "/media/qnap3/Shuxin/SEDA/downloaded_from_SEDA/seda_shapefiles_2019_4.0/"
shapefile <- st_read(paste0(dir_data, "seda_shapefiles_2019_4.0.shp"))
```

```{r}
class(shapefile)
st_geometry_type(shapefile)
(shapefile_geom <- st_geometry(shapefile))
```

```{r}
# par(mar = c(0,0,1,0))
# plot(shapefile[1], reset = FALSE) # reset = FALSE: we want to add to a plot with a legend
# plot(shapefile[1,1], col = 'grey', add = TRUE)
```
```{r}
library(foreign) # open the .dbf file

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
